X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on a conventional source

### 2014-04-15 hedpc.tex
spell check

Our design introduces edge-on illuminated,  circularly aligned structures. Edge-on illumination
(Fig.~\ref{Fig:schematic}), as
opposed to face-on illumination, exploits the dimension along the grating
lines to form a high aspect ratio of the structures in the direction of the beam. The
effective structure height of the grating is then determined by the grating
dimension along the grating lines, which essentially allows arbitrarily high
aspect ratios. 
\begin{figure}[h!]
    \centering
    \includegraphics[width=.7\textwidth]{figures/figure1.eps}
    \caption{Schematic of a grating
        interferometer for X-ray energies between 60 and
        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
        aspect ratio is defined by the ratio of the travelling distance along the
        grating lines and the period and can be arbitrarily long. In order to maximise
        the field of view, the grating structures are aligned on an
        arc. A \SI{100}{\kilo\eV} setup was realised where the distance
        between the source and the source grating is \SI{23}{\centi\metre}
    and the distance between the source grating and the phase grating is
    \SI{16}{\centi\metre}. That is also the distance from the phase grating
to the analyzer grating.}%
\label{Fig:schematic}
\end{figure}

@@

Possible usages of edge-on grating interferometry encompass applications
ranging from medical imaging to non-destructive testing and homeland
security. All these applications seek for high (greater than
\SI{100}{\kilo\eV}) nominal energies
and compact designs. Particularly for medical application, the operation of
a phase contrast imaging device at high energies is imperative. When imaging
patients, a crucial issue is the dose, which depends mainly on the
absorption of the X-rays and decreases with the third power of the photon
energy~\cite{Momose2005}. On the other hand, the phase interaction is only inversely
proportional to the energy and is therefore relatively much more relevant
than absorption as the energy increases, possibly leading to a decreased
exposure for an equivalent image quality. Clinical operation of such a
device will imply measuring patients who normally breath, move and shake.
Fast acquisitions are therefore required, in order to keep the images sharp
and artefact free. As a consequence, compact, efficient imaging systems need
to be developed to provide imaging capabilities at sufficient speed. Our
circular grating alignment matches the structures of the diffracting and
absorbing elements to the divergent beam, especially for compact geometries.
In conclusion, short, high-energy phase-contrast systems will enable the
efficient investigation of high-density materials or thick samples, adding
information on electron density and integrated small-angle scattering power
to the conventional absorption-based signal. This will improve material
discrimination and density sensitivity in future X-ray or even
neutron~\cite{Grunzweig2008} investigations.

@@

\section*{Acknowledgements}
We thank Gordan Mikuljan, Peter Modregger and István Mohácsi from the Paul
Scherrer Institute (PSI), Switzerland, for the
work on the mechanical design, the scientific advice, and the \ac{SEM} images
respectively, Joachim Schulz and Marco Walter from
Microworks GmbH, Germany, for the competent support on grating design
issues, Christian Kottler and Vincent Revol from Centre Suisse
d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
discussions on the design of the system. This work has been partially
supported by the Competence Centre for Materials Science and Technology
(CCMX) of the ETH Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.

>>>>

Our design introduces edge-on illuminated,  circularly aligned structures. Edge-on illumination
(Fig.~\ref{Fig:schematic}), as
opposed to face-on illumination, exploits the dimension along the grating
lines to form a high aspect ratio of the structures in the direction of the beam. The
effective structure height of the grating is then determined by the grating
dimension along the grating lines, which essentially allows arbitrarily high
aspect ratios. 
\begin{figure}[h!]
    \centering
    \includegraphics[width=.7\textwidth]{figures/figure1.eps}
    \caption{Schematic of a grating
        interferometer for X-ray energies between 60 and
        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
        aspect ratio is defined by the ratio of the traveling distance along the
        grating lines and the period and can be arbitrarily long. In order to maximize
        the field of view, the grating structures are aligned on an
        arc. A \SI{100}{\kilo\eV} setup was realized where the distance
        between the source and the source grating is \SI{23}{\centi\metre}
    and the distance between the source grating and the phase grating is
    \SI{16}{\centi\metre}. That is also the distance from the phase grating
to the analyzer grating.}%
\label{Fig:schematic}
\end{figure}

@@

Possible usages of edge-on grating interferometry encompass applications
ranging from medical imaging to non-destructive testing and homeland
security. All these applications seek for high (greater than
\SI{100}{\kilo\eV}) nominal energies
and compact designs. Particularly for medical application, the operation of
a phase contrast imaging device at high energies is imperative. When imaging
patients, a crucial issue is the dose, which depends mainly on the
absorption of the X-rays and decreases with the third power of the photon
energy~\cite{Momose2005}. On the other hand, the phase interaction is only inversely
proportional to the energy and is therefore relatively much more relevant
than absorption as the energy increases, possibly leading to a decreased
exposure for an equivalent image quality. Clinical operation of such a
device will imply measuring patients who normally breath, move and shake.
Fast acquisitions are therefore required, in order to keep the images sharp
and artifact free. As a consequence, compact, efficient imaging systems need
to be developed to provide imaging capabilities at sufficient speed. Our
circular grating alignment matches the structures of the diffracting and
absorbing elements to the divergent beam, especially for compact geometries.
In conclusion, short, high-energy phase-contrast systems will enable the
efficient investigation of high-density materials or thick samples, adding
information on electron density and integrated small-angle scattering power
to the conventional absorption-based signal. This will improve material
discrimination and density sensitivity in future X-ray or even
neutron~\cite{Grunzweig2008} investigations.

@@

\section*{Acknowledgements}
We thank Gordan Mikuljan, Peter Modregger and István Mohácsi from the Paul
Scherrer Institute (PSI), Switzerland, for the
work on the mechanical design, the scientific advice, and the \ac{SEM} images
respectively, Joachim Schulz and Marco Walter from
Microworks GmbH, Germany, for the competent support on grating design
issues, Christian Kottler and Vincent Revol from Centre Suisse
d'\'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
discussions on the design of the system. This work has been partially
supported by the Competence Centre for Materials Science and Technology
(CCMX) of the ETH Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.
